### 2019-06-08 doc/chapters/challenge_stainless.tex
typos

So we can not know how many errors will face us.
Lets go another way, because the errors may take too much time and it might lead to a next error.
We extract the code needed to verify a transaction mainly the class Transaction and ScriptInterpreter with many other classes their depending on.

@@

So the sbt plugin does not complain always where the JAR file did.
The open \href{https://github.com/epfl-lara/stainless/issues/484}{issue \mypound484 on GitHub} might describe exactly this error.

>>>>

So we can not know how many errors will face us.
Let's go another way, because the errors may take too much time and it might lead to a next error.
We extract the code needed to verify a transaction mainly the class Transaction and ScriptInterpreter with many other classes their depending on.

@@

So the sbt plugin does not always complain where the JAR file did.
The open \href{https://github.com/epfl-lara/stainless/issues/484}{issue \mypound484 on GitHub} might describe exactly this error.
